### 2014-03-16 src/discussion.Rnw
.

\section{Discussion}
\label{sec:discussion}

@@

% About Randoop and Original
Analysing the scores further, we note that the accuracy of prediction
($R^2$) achieved by sampling is generally lower for generated test
suites. As the sampling denominator increases, the correlation
reduces drastically for generated test suites while correlation remains strong
for original test suites
Secondly, we also observe that the multiplier factor $\beta_1$ 
is smaller for generated test suites than original test suites. This
observation holds good for all sampling and operator selection strategies
examined.  Both these factors together suggest that generated
test suites have a higher variability in their sampled mutation scores than
original test suites. We note that since $\beta_1$ was generally smaller
for generated test suites than original test suites, the full mutation score
corresponding to a sampled mutation score for generated test suites would
be lower than what would be expected from the original test suite.
Secondly, the amount of reduction that can be gained by sampling that must reach a given correlation is lower for generated test suites.

@@

For line count strategies, only the external sampling produced
consistent results, which were again not as good as \textit{round(x)}
for similar reduction ratios. Secondly, we had hypothesised
that coverage was a significant contributor to having a high
correlation with the full mutation score. However we could find no
evidence in support of this hypothesis with line, method, class, and
project scope showing similar correlation and consistency at similar
reduction ratios.

>>>>

section{Discussion}
\label{sec:discussion}

@@

% About Randoop and Original
Analyzing the scores further, we note that the accuracy of prediction
($R^2$) achieved by sampling is generally lower for generated test
suites. As the sampling denominator increases, the correlation
reduces drastically for generated test suites while correlation remains strong
for original test suites
Secondly, we also observe that the multiplier factor $\beta_1$ 
is smaller for generated test suites than original test suites. This
observation holds good for all sampling and operator selection strategies
examined.  Both these factors together suggest that generated
test suites have a higher variability in their sampled mutation scores than
original test suites. We note that since $\beta_1$ was generally smaller
for generated test suites than original test suites, the full mutation score
corresponding to a sampled mutation score for generated test suites would
be lower than what would be expected from the original test suite.
Secondly, the amount of reduction that can be gained by sampling that must reach a given correlation is lower for generated test suites.

@@

For line count strategies, only the external sampling produced
consistent results, which were again not as good as \textit{round(x)}
for similar reduction ratios. Secondly, we had hypothesized
that coverage was a significant contributor to having a high
correlation with the full mutation score. However we could find no
evidence in support of this hypothesis with line, method, class, and
project scope showing similar correlation and consistency at similar
reduction ratios.
